Learning Causally-Generated Stationary Time Series

### 2017-02-24 doc/paper.tex
Rephrasing in abstract
Rephrasing of captions of fig 1 and 2

\usepackage{icml2017}  % option: accepted
\icmltitlerunning{Learning Causally-Generated Stationary Time Series}

@@

\begin{abstract}
We investigate the notion of causality in modelling stationary time series. Extending on the work by \citet{Tobar:2015:Learning_Stationary}, we present the Causal Gaussian Process Convolution Model (CGPCM). The CGPCM models the kernel of a Gaussian process nonparametrically and has an inductive bias towards causally-generated time series. We develop an algorithm to perform inference and demonstrate the CGPCM on synthetic and real-world signals.
\end{abstract}

@@

\section{Modelling Causally-Generated Stationary Time Series}
%
Consider modelling a stationary time series $f$. Motivated by the fact that many dynamical systems in nature can accurately be described by an initial value problem or a linear system, we let $f$ be the solution of a time-invariant linear initial value problem with causal Green's function $h$ and forcing function $x$, or equivalently the system response of a time-invariant linear system with causal impulse response $h$ and excitation $x$. It then holds that
\begin{align} \label{eq:model}
    f(t) = \int^t h(t- \tau)x(\tau)\id{\tau}.
\end{align}
For parsimony, we denote integration from negative infinity or to positive infinity by omitting the respective limit from the integral throughout.
Note that $f(t)$ depends on $x(\tau)$ only for $\tau \le t$; this reveals \cref{eq:model}'s causal nature.

@@

\begin{figure}[t]
    \centering
    \begin{tabularx}{\linewidth}{>{\centering}X>{\centering}X}
        GPCM & CGPCM
    \end{tabularx}
    \includegraphics[width=\linewidth, height=3cm]{resources/cropped/prior.pdf}
    \caption{Prior distribution over kernels in the GPCM and CGPCM. Lines correspond to means and gradients correspond to uncertainty.}
    \label{fig:prior}
\end{figure}
\begin{figure}[t]
    \centering
    \begin{tabularx}{\linewidth}{>{\centering}X>{\centering}X}
        ~~GPCM & ~~~~~~CGPCM
    \end{tabularx}
    \includegraphics[width=\linewidth, height=3cm]{resources/cropped/prior_psd.pdf}
    \caption{Prior distribution over PSDs in the GPCM and CGPCM. The unit on the $y$ axis is decibel. Lines correspond to means and gradients correspond to uncertainty.}
    \label{fig:prior_psd}
\end{figure}

>>>>

\usepackage[accepted]{icml2017}  % option: accepted
\icmltitlerunning{Learning Causally-Generated Stationary Time Series}

@@

\begin{abstract}
We investigate the notion of causality in modelling stationary time series. Extending on the work by \citet{Tobar:2015:Learning_Stationary}, we present the Causal Gaussian Process Convolution Model (CGPCM). The CGPCM models the kernel of a Gaussian process nonparametrically and has an inductive bias towards causally-generated time series. We develop enhanced variational inference and learning schemes and demonstrate the CGPCM on synthetic and real-world signals.
\end{abstract}

@@

\section{Modelling Causally-Generated Stationary Time Series}
%
Consider modelling a stationary time series $f$. Motivated by the fact that many dynamical systems in nature can accurately be described by an initial value problem or a linear system, we let $f$ be the solution of a time-invariant linear initial value problem with causal Green's function $h$ and forcing function $x$, or equivalently the system response of a time-invariant linear system with causal impulse response $h$ and excitation $x$. It then holds that
\begin{align} \label{eq:model}
    f(t) = \int^t h(t- \tau)x(\tau)\id{\tau}.
\end{align}
For parsimony, we denote integration from negative infinity and to positive infinity by omitting the respective limit from the integral throughout.
Note that $f(t)$ depends on $x(\tau)$ only for $\tau \le t$; this reveals \cref{eq:model}'s causal nature.

@@

\begin{figure}[t]
    \centering
    \begin{tabularx}{\linewidth}{>{\centering}X>{\centering}X}
        GPCM & CGPCM
    \end{tabularx}
    \includegraphics[width=\linewidth, height=3cm]{resources/cropped/prior.pdf}
    \caption{Prior distribution over kernels in the GPCM and CGPCM. Lines correspond to means and gradients indicate marginal variance.}
    \label{fig:prior}
\end{figure}
\begin{figure}[t]
    \centering
    \begin{tabularx}{\linewidth}{>{\centering}X>{\centering}X}
        ~~GPCM & ~~~~~~CGPCM
    \end{tabularx}
    \includegraphics[width=\linewidth, height=3cm]{resources/cropped/prior_psd.pdf}
    \caption{Prior distribution over PSDs in the GPCM and CGPCM. The unit on the $y$ axis is decibel. Lines correspond to means and gradients indicate marginal variance.}
    \label{fig:prior_psd}
\end{figure}
